Dominance Regions for Rank Two Cluster Algebras

### 2022-04-05 dominance_regions.tex
Section 4 edits

  \begin{lemma}
    \label{le:transformed inequalities}
    Let $A$ be an invertible $n\times n$ matrix.
    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\bfr\bullet(\bfx-\lambda)\le t$ with $\lambda,\bfr\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet(\bfy-A\lambda)\le t.\]
  \end{lemma}
  \begin{proof}
    This is immediate from the equalities
    \[\bfr\bullet(\bfx-\lambda)=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=(A^{-T}\bfr)\bullet(\bfy-A\lambda).\]
  \end{proof}

  \begin{lemma}
    \label{le:transformed inequalities}
    Let $A=(a_{ij})$ be an invertible $2\times 2$ matrix.
    Under the action of $A$, the region inside $\RR^2$ defined by the inequality $rx+sy\le t$ is transformed to the region defined by the inequality \[\frac{ra_{22}-sa_{21}}{a_{11}a_{22}-a_{12}a_{21}}x + \frac{-ra_{12}+sa_{11}}{a_{11}a_{22}-a_{12}a_{21}}y\le t.\]
  \end{lemma}
  \begin{proof}
    Assume $r,s,t\ne0$, the cases when one of these vanishes follows by the continuity of the transformation.
    Observe that the points $\big(\frac{t}{r},0\big)$ and $\big(0,\frac{t}{s}\big)$ lie on the boundary line of the region defined by the inequality $rx+sy\le t$.
    These are transformed under the action of $A$ into the points $\big(a_{11}\frac{t}{r},a_{21}\frac{t}{r}\big)$ and $\big(a_{12}\frac{t}{s},a_{22}\frac{t}{s}\big)$, respectively, which one readily checks lie along the purported boundary of the image region.
    By the linearity of the transformation of $\RR^2$ given by the matrix $A$, we see that either both the domain region and image region contain the origin or both do not, in particular this implies that the inequalities go in the same direction.
  \end{proof}

  \begin{lemma}
    For $i\ge1$ and $\lambda\in\cI$, the region $\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
    \begin{align}
      \label{ineq:1} u_{i,-}x+u_{i-1,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
      \label{ineq:2} u_{i+1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
      \label{ineq:3} -u_{i-1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
      \label{ineq:4} -u_{i-1,-}x-u_{i-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
    \end{align}

@@

    For $i=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is given by the inequalities 
    \[ (\dagger)\ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
    We inductively compute the region $\phi_{t_{2j}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{t_{2j}}^{-1}=\phi_{t_2}^{-j}$.

    \subsubsection*{Claim:} For $k>0$, $\phi_{t_{2k}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ is the region determined by the inequalities 
    \begin{align*}
      \tag{a} u_{2k,-}x+u_{2k-1,+}y &\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2;\\
      \tag{b} u_{2k+1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
      \tag{c} -u_{2k-1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
      \tag{d} -u_{2k-1,-}x-u_{2k-2,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2.
    \end{align*}

    We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $cx+y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2$ which corresponds to (a) with $k=1$.
    Similarly, the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\dagger$) intersects three domains of linearity in which $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
    By Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with $k=1$.
    This establishes the base of an induction on $k$.

    Assuming the inequalities (a)-(d) hold for $k$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_{t_2}^{-1}$.
    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
    \[u_{2k+2,-}x+u_{2k+1,+}y=(u_{3,+}u_{2k,-}-u_{2,-}u_{2k-1,+})x+(u_{2,+}u_{2k,-}-u_{1,-}u_{2k-1,+})y\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2,\]
    which is the inequality (a) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
    \[-u_{2k+1,-}x-u_{2k,+}y=(-u_{3,+}u_{2k-1,-}+u_{2,-}u_{2k-2,+})x+(-u_{2,+}u_{2k-1,-}+u_{1,-}u_{2k-2,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
    \[u_{2k+3,-}x+u_{2k+2,+}y=(u_{3,+}u_{2k+1,-}-u_{2,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (b) for $k+1$.
    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
    \[-u_{2k+1,-}x-u_{2k,+}y=(u_{1,+}u_{2k-1,-}-u_{2,-}u_{2k,+})x+(-u_{0,+}u_{2k-1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (d) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
    \[-u_{2k+1,-}x+u_{2k+2,+}y=(-u_{1,+}u_{2k+1,-}+u_{0,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (c) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
    \[-u_{2k+1,-}x-u_{2k,+}y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
    This completes the induction on $k$, proving the Claim and the result for $i$ even.

    For $i=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)\subset\RR^2$ is given by the inequalities 
    \[ (\dagger')\ -x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2.\]
    Using that $\phi_{t_{2j+1}}^{-1}=\phi_{t_2}^{-j}\phi_{t_1}^{-1}$, we compute the image inductively as above.
    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_{t_1}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_{t_1}^{-1}$ into the inequality $x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2$.
    The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_{t_1}^{-1}$ and thus produces the inequalities
    \[ cx+y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2 \qquad\text{and}\qquad  y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2.\]

    \subsubsection*{Claim:} For $k\ge 0$, $\phi_{t_{2k+1}}^{-1}\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)$ is the region determined by the inequalities 
    \begin{align*}
      \tag{a$'$} u_{2k+1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
      \tag{b$'$} u_{2k+2,-}x+u_{2k+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
      \tag{c$'$} -u_{2k,-}x+u_{2k+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
      \tag{d$'$} -u_{2k,-}x-u_{2k-1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2.
    \end{align*}
    By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_{t_2}^{-1}$ and this completes the proof.
  \end{proof}

>>>>

  \begin{lemma}
    \label{le:transformed inequalities}
    Let $A$ be an invertible $2\times 2$ matrix.
    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^2$, the region inside $\RR^2$ defined by the inequality $\bfr\bullet(\bfx-\lambda)\le t$ with $\lambda,\bfr\in\RR^2$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet(\bfy-A\lambda)\le t.\]
  \end{lemma}
  \begin{proof}
    This is immediate from the equalities
    \[\bfr\bullet(\bfx-\lambda)=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=(A^{-T}\bfr)\bullet(\bfy-A\lambda).\]
  \end{proof}

  \begin{lemma}
    For $k\ge1$ and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
    \begin{align}
      \label{ineq:1} u_{i,-}x+u_{i-1,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
      \label{ineq:2} u_{i+1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
      \label{ineq:3} -u_{i-1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
      \label{ineq:4} -u_{i-1,-}x-u_{i-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
    \end{align}
    \begin{align}
      \label{ineq:1} u_{k,-}(x-\lambda_1)+u_{k-1,+}(y-\lambda_2) &\le 0;\\
      \label{ineq:2} u_{k+1,-}(x-\lambda_1)+u_{k,+}(y-\lambda_2) &\le 0;\\
      \label{ineq:3} -u_{k-1,-}(x-\lambda_1)+u_{k,+}(y-\lambda_2) &\le cu_{k,+}\lambda_1;\\
      \label{ineq:4} -u_{k-1,-}(x-\lambda_1)-u_{k-2,+}(y-\lambda_2) &\le cu_{k,+}\lambda_1+bu_{k-1,-}\lambda_2.
    \end{align}

@@

    For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
    \[ (\dagger)\ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
    We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.

    \subsubsection*{Claim:} For $i>0$, $\phi_{2i}^{-1}\cC_{2j}(\phi_{2j}\lambda)$ is the region determined by the inequalities 
    \begin{align*}
      \tag{a} u_{2i,-}x+u_{2i-1,+}y &\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2;\\
      \tag{b} u_{2i+1,-}x+u_{2i,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
      \tag{c} -u_{2i-1,-}x+u_{2i,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
      \tag{d} -u_{2i-1,-}x-u_{2i-2,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2.
    \end{align*}

    We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $cx+y\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2$ which corresponds to (a) with $i=1$.
    Similarly, the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\dagger$) intersects the three domains of linearity in which $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
    By Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with $i=1$.
    This establishes the base of an induction on $i$.

    Assuming the inequalities (a)-(d) hold for $k$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_2^{-1}$.
    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
    \[u_{2i+2,-}x+u_{2i+1,+}y=(u_{3,+}u_{2i,-}-u_{2,-}u_{2i-1,+})x+(u_{2,+}u_{2i,-}-u_{1,-}u_{2i-1,+})y\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2,\]
    which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
    \[-u_{2i+1,-}x-u_{2i,+}y=(-u_{3,+}u_{2i-1,-}+u_{2,-}u_{2i-2,+})x+(-u_{2,+}u_{2i-1,-}+u_{1,-}u_{2i-2,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
    \[u_{2i+3,-}x+u_{2i+2,+}y=(u_{3,+}u_{2i+1,-}-u_{2,-}u_{2i,+})x+(u_{2,+}u_{2i+1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (b) for $i+1$.
    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
    \[-u_{2i+1,-}x-u_{2i,+}y=(u_{1,+}u_{2i-1,-}-u_{2,-}u_{2i,+})x+(-u_{0,+}u_{2i-1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (d) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
    \[-u_{2i+1,-}x+u_{2i+2,+}y=(-u_{1,+}u_{2i+1,-}+u_{0,-}u_{2i,+})x+(u_{2,+}u_{2i+1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
    \[-u_{2i+1,-}x-u_{2i,+}y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
    This completes the induction on $i$, proving the Claim and the result for $k$ even.

    For $k=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
    \[ (\dagger')\ -x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2.\]
    Using that $\phi_{2j+1}^{-1}=\phi_2^{-j}\phi_1^{-1}$, we compute the image inductively as above.
    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_1^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_1^{-1}$ into the inequality $x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2$.
    The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_1^{-1}$ and thus produces the inequalities
    \[ cx+y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2 \qquad\text{and}\qquad  y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2.\]

    \subsubsection*{Claim:} For $i\ge 0$, $\phi_{2i+1}^{-1}\cC_{2j+1}(\phi_{2j+1}\lambda)$ is the region determined by the inequalities 
    \begin{align*}
      \tag{a$'$} u_{2i+1,-}x+u_{2i,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
      \tag{b$'$} u_{2i+2,-}x+u_{2i+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
      \tag{c$'$} -u_{2i,-}x+u_{2i+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
      \tag{d$'$} -u_{2i,-}x-u_{2i-1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2.
    \end{align*}
    By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_2^{-1}$ and this completes the proof.
  \end{proof}
